COG-ED Manuscript

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
added authornote for corresponding author info

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
      - Visualization
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
abstract: |
  When individuals set goals, they consider the subjective value (SV) of both the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  However, the SV of effort is highly individual, and previous quantification approaches have had two crucial limitations: They presumed a unidirectional relationship between objective task load and the SV of effort, and as a consequence, they could only quantify the SVs of tasks with an objective order of task load.
  One of these approaches is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013).
  We aim to replicate their analysis with our adaptation, the Cognitive and Emotion Regulation Effort Discounting (CERED) paradigm.
  We argue that the CERED paradigm allows two crucial things: Quantifying SVs without assuming that the easiest level is preferred, and quantifying SVs for tasks with no objective order of task load.

>>>>

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
      - Visualization
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
abstract: |
  When individuals set goals, they consider the subjective value (SV) of both the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  However, the SV of effort is highly individual, and previous quantification approaches have had two crucial limitations: They presumed a unidirectional relationship between objective task load and the SV of effort, and as a consequence, they could only quantify the SVs of tasks with an objective order of task load.
  One of these approaches is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013).
  We aim to replicate their analysis with our adaptation, the Cognitive and Emotion Regulation Effort Discounting (CERED) paradigm.
  We argue that the CERED paradigm allows two crucial things: Quantifying SVs without assuming that the easiest level is preferred, and quantifying SVs for tasks with no objective order of task load.
